Over-relaxed Sinkhorn's Algorithm for Regularized Optimal Transport

### 2017-10-13 paper.tex
Algo

Perspectives:
global convergence, how chosing $\omega$?, intensive numerical study with respect to other accelerarions methods\cite{}.

>>>>

Perspectives:
global convergence, how chosing $\omega$?, intensive numerical study with respect to other accelerarions methods\cite{2016arXiv160604133S,2017arXiv170509634A}.
